Presolving for\\ Mixed-Integer Semidefinite Optimization

### 2020-12-14 tex/MISDP-Presolving/MISDPpresolving.tex
add remark about Gershgorin for SDPrank1-constraints

>>>>

\begin{remark}
  This idea can be used to detect a cut off for an SDP-constraint that
  should have rank 1. Recall that a positive semidefinite matrix has rank 1
  if and only if all of its 2 by 2 minors are zero. This implies that the
  smallest eigenvalue of each 2 by 2 submatrix needs to be 0. Thus, if
  there exist two indices~$i$, $k$, so that
  \begin{align*}
    0 \notin D_i,\quad 0 \notin D_k, \quad D_i \cap D_k = \varnothing,
  \end{align*}
  then the current node can be cut off, since a minimal eigenvalue of 0 is
  not obtainable for the 2 by 2 submatrix indexed by~$(i,k)$.

  In the case of a dual SDP-constraint~$A(y) \geq 0$, the Gershgorin
  discs~$D_i$, $D_k$ do not contain 0, if the lower bounds~$\ell_i$,
  $\ell_k$ of the entries~$A(y)_{ii}$ and~$A(y)_{kk}$ are strictly
  positive, and if the radius of the discs is strictly smaller
  than~$\ell_i$, $\ell_k$, i.e.,
  \begin{align*}
    \ell_i > 0,\quad \ell_k > 0, \qquad \sum_{j\neq i} \abs{A(y)_{jj}} <
    \ell_i, \quad \sum_{j\neq k} \abs{A(y)_{jj}} < \ell_k.
  \end{align*}
  Currently, this is not implemented for SDP-constraints with an additional
  rank-1 constraint.
\end{remark}
